
Title: 'Market Basket Analysis - Association Rule using Apriori Algorithm'
author: "Kaycee"
date: "10/9/2019"
output: html_document
---

```{r}
library(RMySQL)

#Import df 'line_item'

# Settings

db_user <- 'data_student_berlin'

db_password <- 'waai_has_shitty_internet'

db_name <- 'pricehub'

db_table <- 'line_item'

db_host <- '34.89.228.59' # for local access

db_port <- 3306

# Read data from db

mydb <-  dbConnect(MySQL(), user = db_user, password = db_password,
                   
                   dbname = db_name, host = db_host, port = db_port)

s <- paste0("select * from ", db_table)

rs <- dbSendQuery(mydb, s)

line_item <-  fetch(rs, n = -1)

##Import df 'orders'
#  Settings

db_table <- 'orders'

#  Read data from db

s <- paste0("select * from ", db_table)

rs <- dbSendQuery(mydb, s)

orders <-  fetch(rs, n = -1)

#Import df 'products'

db_table <- 'products'

#Read data from db

s <- paste0("select * from ", db_table)

rs <- dbSendQuery(mydb, s)

products <-  fetch(rs, n = -1)

on.exit(dbDisconnect(mydb))
```
Library Loading.
```{r}
#library(RMySQL)
#library(dplyr)
#library(ggplot2)
#library(arules)
#library(skimr)
#library(mbar)
#library(plyr)
#library(arulesViz)
```
#EDA
```{r}
head(line_item)
head(orders)
head(products)
```
#Check that all orders in line_item are present in our orders dataset
```{r}
library(dplyr)
New_line_item <- inner_join(line_item, orders, by = "id_order")
head(New_line_item)
glimpse(New_line_item)
```
## Creating a new column called totalQuantitypaid (unit_price*product_quanity)
```{r}
New_line_item <- New_line_item %>% 
  mutate(PQ_price = unit_price * product_quantity) 
head(New_line_item)
```
## Grouping and summarising using id_order $ total_paid
```{r}
Sum_Total_Paid <-New_line_item %>% 
  group_by(id_order) %>% 
  summarise(total_paid_li = sum(PQ_price))
head(Sum_Total_Paid)
```
## Joining orders, New_line_sum and grouping by "id_order"
```{r}
Final<- inner_join(orders, Sum_Total_Paid, by = "id_order")
dim(Final)
```
## Relationship without Prices in Order and lineitems using GGPLOT
```{r}
library(ggplot2)
ggplot(data=Final, aes(total_paid_li, total_paid)) + 
  geom_point(aes(col="pink", fill= '.count..')) 

qplot(Final$total_paid_li, geom = "histogram", binwidth = 50, 
      main = "Histogram of Total price of Line Item", xlab = "Total Line Item price Paid", 
      fill = ..count.., xlim=c(0,3000)) + scale_fill_gradient("Count", low = "green", high = "red")
```
## Exclude from line_item any rows from orders that are not “Completed
```{r}
New_line_item_completed <- filter(Final, state == "Completed")

completedstate <- New_line_item %>% select(state) %>% filter(state =="Completed")
head(completedstate)

CancelledState <-Final %>% select(state) %>% filter(state =="Cancelled")

head(CancelledState)
```
# Exclude from line_item any rows that do not meet that condition.
```{r}
Excluded_row <- nrow(line_item) - nrow(New_line_item)

head(Excluded_row)
```
## Explore the relationship between prices in line_item and product
```{r}

#EDA 
tbl_df(products)
data.frame(products)
dim(products)

# Checking that all sku in New_line_item and products dataset. 
Product_line_item<- inner_join(New_line_item, products, by = "sku")

head(Product_line_item)

## Creating a column Called PQ_Paid in line_item of products
Product_line_item <- Product_line_item %>% 
  mutate(Paid_PQ = unit_price*product_quantity)


## Exporing relationship between the prices of line_item and products using ggplot

Product_line_item %>% ggplot(aes(total_paid, Paid_PQ)) +  geom_point()

Product_line_item %>% ggplot(aes(total_paid, price, col= "unit_price" , size=1)) +  
  geom_point() +  theme_bw()
```

```{r}
# CLEANING AND PREPROCESSING MY FINAL DATAFRAME 
Final_data<- select(Product_line_item, sku, name_en, short_desc_en, price, brand, 
                    manual_categories,total_paid, Paid_PQ, 
                    product_quantity, unit_price,
                    id_order)
glimpse(Final_data)

```
# REMOVING OUTLIERS FROM OUR PRICE DATASET
```{r}

Outlier_Unit_price <- boxplot(Final_data$unit_price, plot = FALSE)$out

Outlier_Paid_PQ <- boxplot(Final_data$Paid_PQ, plot = FALSE)$out

Outlier_price <- boxplot(Final_data$price, plot = FALSE)$out

Outlier_total_paid <- boxplot(Final_data$total_paid, plot = FALSE)$out


Final_data[which(Final_data$unit_price %in% 
                   Outlier_Unit_price),]

Final_data[which(Final_data$price %in% 
                   Outlier_price),]


Final_data[which(Final_data$total_paid %in% 
                   Outlier_total_paid),]

Final_data[which(Final_data$Paid_PQ %in% 
                   Outlier_Paid_PQ),]

# REMOVING PRICES OUTLIERS FROM THE DATASET

Final_data <-Final_data[-which(Final_data$unit_price %in% Outlier_Unit_price),]

Final_data <- Final_data[-which(Final_data$price %in% Outlier_price),]

Final_data <- Final_data[-which(Final_data$total_paid %in% Outlier_total_paid),]

Final_data <- Final_data[-which(Final_data$Paid_PQ %in% Outlier_Paid_PQ),]

# CHECKING RELATIONSHIP BLW PRICES IN OUR DATASET 
ggplot(Final_data, aes(total_paid, Paid_PQ, color= "blue")) + geom_point()
```
# CREATING A TRANSACTIONAL FILE
```{r}
Data <- select(Final_data,manual_categories,id_order)


write.csv( Final_data, "Data.csv", row.names = FALSE)
Sys.sleep(10)

get_data <- read.transactions("Data.csv",
                              format = "single", header= T,
                              sep = ",",
                              cols = c("id_order", "manual_categories"))

# Summary of get_data 
cat("Number of basket:", length(get_data))
cat("Number of unique items:", sum(size(get_data)))

summary(get_d1ata)

inspect(get_data[1:10])

length(get_data)

size(get_data)

head(itemLabels(get_data))

# Summary of the number of support/frequency labels of items in the basket
itemFrequency(get_data[,1:10])

```
## Visualization of items in the Dataset 
```{r}
itemFrequencyPlot(get_data, topN=10, type="relative",col= "pink",
                  main = "Relative Item Frequency Plot")

# Visualizing using support frequency.
itemFrequencyPlot(get_data, support= 0.5)

# Using Image() function to visualize

image(get_data)
```
# APPLYING APRIORI ALGORITHM
```{r}
Data_rules <- apriori(get_data) 

Data_rules <- apriori(get_data,parameter = list(minlen= 2, maxlen= 10,
                                                sup = 0.00001, conf = 0.5))
summary(Data_rules)
inspect(Data_rules[1:10])

# SORTING BY SUPPORT, CONF, AND LIFT

Data_rules<- sort(Data_rules, by = "conf", decreasing = T) 

inspect(Data_rules)

#Finding duplicates in our Data_rules dataset 
redundant_rules<- is.redundant(Data_rules)
summary(redundant_rules)


# Removing the duplicated rule in Data_ruless
Data_rules <- Data_rules[!redundant_rules]
summary(Data_rules)


# Plot a graph of our Data_rules Dataset

plot(Data_rules, method = "graph", interactive = T)

plot(Data_rules, method = "grouped")

plot(Data_rules, method="paracoord",  control=list(alpha=.5, reorder=TRUE))


plot(Data_rules,measure=c("support","lift"), shading = "confidence",interactive=T) 

# Changing default to RHS

Data_rules_accessories <- apriori(get_data,parameter= list(support= .00005, conf =0.05),
                                  appearance = list(default = 'rhs', lhs = "accessories"))

inspect(Data_rules_accessories)
```

